### 2020-01-10 paper/sex_selection_spacing-ver3.tex
Begin discussion of TFR vs hazard model predictions

>>>>

One of the effects of the increasing use of sex selection over time is that the total 
fertility rate will tend to overestimate the decline in fertility.
``Tempo'' effects, such as those that arise from postpone of childbearing, are studied 
extensively in the literature \citep{Bongaarts1999}.
With development, women tend to have their first child later as a result of increasing 
years spent in school and later marriage, but, as discussed above, spacing between births 
also tend to shorten as women become more likely to join the labor market, which will 
tend to counter the downward effect on the TFR.

India has also seen an increasing age of marriage, but birth spacing has also become
much longer as women leave the labor market and there is substantial use of 
sex selection.
The result is that the TFR becomes an increasingly biased measure of cohort fertility
\citep{Ni-Bhrolchain2011}.

To understand how strong the bias from sex selection on TFR is and how cohort fertility
has changed, I compare predicted fertility using both TFR and the model results
presented above.
